
```{r}
library("kernlab")
```


```{r}
bestAccuracy=0
bestKernel=""
bestNu=0
bestEpsilon=0
bestSample=0
kernelList=c("rbfdot","polydot","tanhdot","vanilladot","laplacedot","anovadot")
```
```{r}
library(openxlsx)
library(readxl)
myData1<-read.xlsx("E:/TIET/6th sem/Predictive Analytics using Statistics/Adult.data")
myData<-as.data.frame(myData1)
myData<-as.data.frame(sapply(myData,as.numeric))
head(myData)

```
```{r}
sample <- sample(c(TRUE, FALSE), nrow(myData), replace=TRUE, prob=c(0.7,0.3))
train  <- myData[sample, ]
test   <- myData[!sample, ]

```


```{r}
fitnessFunction<-function(k,n,e,train,test)
{
  
  trainX=train[,1:23]
  trainY=as.factor(train[,24:24])
  
  testX=test[,1:23]
  testY=as.factor(test[,24:24])
  model<-ksvm(as.matrix(trainX),(trainY),kernel=k,nu=n,espilon=e)
  predicted<-predict(model,testX)
  
 accuracy<-sum(as.numeric(predicted)==as.numeric(testY))
 accuracy<-accuracy/nrow(test)
  return (round(accuracy,2))
}
```

```{r}
metrics<-data.frame(iteration<-c(),accuracy<-c())
```

```{r}
for(k in 1:10)
{
  sample <- sample(c(TRUE, FALSE), nrow(myData), replace=TRUE, prob=c(0.7,0.3))
train  <- myData[sample, ]
test   <- myData[!sample, ]
  for(i in 1:1000)
  {
    k=sample(kernelList,1)
    
    n=runif(1)
    e=runif(1)
    Accuracy=fitnessFunction(k,n,e,train,test)
    print(Accuracy)
    newRow<-data.frame(iterations=1,b=Accuracy)
   metrics<-rbind(metrics,newRow);
    if(Accuracy>bestAccuracy)
    {
      bestKernel=k
      bestNu=n
      bestEpsilon=e
      bestAccuracy=Accuracy;
      
    }
    else{
      
    }
  }
}
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
